The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-08-11 paper/paper.Rmd
Update manuscript

```{r scbi-spatial-cross-validation-schematic, out.width="66%", fig.cap= "Schematic of spatial cross-validation. Using the k = 1 fold (bottom-left) as the test set, k = 2 through 4 as the training set, along with a \"fold buffer\" extending outwards from the test set to maintain spatial independence between it and the training set.", echo = FALSE}
fold_number <- 1

@@

```{r appendix2-plot, out.width="100%", fig.cap="Cross-validated RMSE estimates for 5 competitive distances2.", echo = FALSE}
mult_dist_comp %>%
  ggplot(aes(dist, rmse)) +
  geom_point() +
  xlab("Distance (m)") +
  ylab("RMSE (cm)")
```

>>>>

```{r scbi-spatial-cross-validation-schematic, out.width="66%", fig.cap= "Schematic of spatial cross-validation. Using the k = 1 fold (bottom-left) as the test set, k = 2 through 4 as the training set, along with a fold buffer extending outwards from the test set to maintain spatial independence between it and the training set.", echo = FALSE}
fold_number <- 1

@@

```{r appendix2-plot, out.width="100%", fig.cap="Cross-validated RMSE estimates for 5 competitive distances.", echo = FALSE}
mult_dist_comp %>%
  ggplot(aes(dist, rmse)) +
  geom_point() +
  xlab("Distance (m)") +
  ylab("RMSE (cm)")
```
